Design and Implementation of Probabilistic Programming Language Anglican

### 2016-07-05 paper/paper.tex
more citations

While probabilistic programming systems shorten the iteration cycle in
exploratory model design, they typically lack basic functionality needed for
data I/O, pre-processing, and analysis and visualization of inference results.
In this demonstration, we describe the implementation of
Anglican~(\cite{TMW15}), a probabilistic
programming language that tightly integrates with
Clojure~(\url{http://clojure.org/}), a general-purpose programming language
that runs on the Java Virtual Machine (JVM). Both languages share a common
syntax, and can be invoked from each other. This allows Anglican programs to
make use of a rich set of libraries written in both Clojure and Java.
Conversely Anglican allows intuitive and compact specification of models for
which inference may be performed as part of a larger Clojure project.

@@

>>>>

While probabilistic programming systems shorten the iteration cycle in
exploratory model design, they typically lack basic functionality needed for
data I/O, pre-processing, and analysis and visualization of inference results.
In this demonstration, we describe the implementation of
Anglican~(\cite{TMW15, Anglican}), a probabilistic
programming language that tightly integrates with
Clojure~\cite{H08,Clojure}, a general-purpose programming language
that runs on the Java Virtual Machine (JVM). Both languages share a common
syntax, and can be invoked from each other. This allows Anglican programs to
make use of a rich set of libraries written in both Clojure and Java.
Conversely Anglican allows intuitive and compact specification of models for
which inference may be performed as part of a larger Clojure project.

@@

\section{Anglican Syntax}

\cite{SDF+10, PC94, H08}
